Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-06 appendix.tex
tex
svg

\newpage
\appendix

@@

@@

@@

\section{Miscellaneous}

\textbf{Societal Impact.}
%
As encouraged by the author guidelines, we briefly discuss the potential
societal impact of our work.
%
Adversarial attacks may raise \uline{security considerations} on deep learning
applications, and even cause negative effect.
%
In contrast, in this manuscript, we focus on defending against the attacks and
enhancing a model's adversarial robustness, and hence is expected to have a
positive impact instead.
%
Besides, although adversarial training is not \uline{environment-friendly} due
to its high training cost in GPU time, our study has significantly improved the
adversarial training efficiency compared to the previous works.

>>>>

\clearpage
\appendix

\section{Supplementary Information}

\noindent\textbf{I. Potential Societal Impact.}

(1) Security: Adversarial attacks may raise security considerations on deep
learning applications, and even cause negative effect.
%
In contrast, in this manuscript, we focus on defending against the attacks and
enhancing a model's adversarial robustness, and hence is expected to have a
positive impact instead.

(2) Environment: Although adversarial training is not environment-friendly due
to its high training cost (in terms of more intensive computation than regular
training), our method has significantly improved the adversarial training
efficiency compared to the previous works (hence is a little bit more
environment-friendly).

@@

	\item Gradient in figure 5?

@@

	\item Why not wall time as training cost?

	\item the destination hardness is semihard (or something between semihard
		and softhard, we leave new sampling strategy for future work).

	\item Note, naive combination of benign training and adv train does not lead to better
result, why? mix 0.5

	\item why experiment, 8 step by default

@@
